Modeling thermal dust emission in the {\it PLANCK} 2015 release maps

### 2015-06-20 ms.tex
added Table 2 with 2015 release values

>>>>

\begin{center}
\begin{deluxetable*}{llrrrrrrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{11} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters (2015 release)} 
\tablehead{
\colhead{Number} &
\colhead{Model} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$} &
\colhead{$T_2$} &
\colhead{$T_1$} &
\colhead{$n$} &
\colhead{D.O.F.} &
\colhead{$\chi^2$} &
\colhead{$\chi^2_{\nu}$}
}
\startdata
 1 & FDS99 best-fit  & \textcolor{blue}{0.0363} & \textcolor{blue}{13.0} & \textcolor{blue}{1.67} & \textcolor{blue}{2.70} & \textcolor{red}{15.67} &  \textcolor{red}{9.12} & \textcolor{red}{1.055} & \textcolor{blue}{7} & \textcolor{red}{55.0} & \textcolor{red}{7.86} \\
 2 & FDS99 general   & \textcolor{red}{0.0457}  & \textcolor{red}{8.03}  & \textcolor{red}{1.59}  & \textcolor{red}{2.83}  & \textcolor{red}{15.68} &  \textcolor{red}{9.71} & \textcolor{red}{0.998} & \textcolor{blue}{3} & \textcolor{red}{6.42} & \textcolor{red}{2.14} \\
 3 & single MBB      & \textcolor{blue}{0.0}    &  ...                   &  ...                   & \textcolor{red}{1.56}  & \textcolor{red}{19.86} &   ...                  & \textcolor{red}{1.016} & \textcolor{blue}{6} & \textcolor{red}{48.0} & \textcolor{red}{7.99} \\ %[-2ex]
\enddata
\end{deluxetable*}
\end{center}
